### 2013-02-14 doc/xps2013/proposal.tex
edits all over

The PIs organize their joint research activity under the umbrella of
the ``SAMPA group'' (SAfe MultiProcessing Architectures).  Some brief
statistics help summarize the group's size, strength, and focus:
\begin{itemize}
\item There are roughly ten graduate students, most actively
  coadvised.
\item In the last five years, the group has produced fifteen papers
  published in ASPLOS, ISCA, PLDI, OOPSLA, MICRO, and OSDI as well as three
  papers in the USENIX Workshop on Hot Topics in Parallelism.
\end{itemize}
The SAMPA group is an ideal size for collaboration across the system
execution stack from computer architecture up through software
engineering.  Compared to large collaborations with several faculty,
there are no graduate students (or faculty) who specialize entirely in
particular subtopics.  The students gain expertise across
computer-science disciplines and use appropriate ideas from hardware,
software, theory, etc. to solve research problems.

@@

\begin{itemize}
\item PI Oskin will focus on communication issues. 
\item PI Ceze will focus on compiler and programming languages work.
\item PI Kahan will focus on organizing benchmarks and performance evaluation efforts.
\item All PIs expect to solicit guidance and collaboration from
  researchers such as John Feo (PNNL), Jim Larus (Microsoft Research), Hans
  Boehm (HP Research), and Preston Briggs,  with whom
  they have already collaborated on other projects.
\end{itemize}

>>>>

The PIs organize their joint research activity under the umbrella of
the ``SAMPA group'' (SAfe MultiProcessing Architectures).  Some brief
statistics help summarize the group's size, strength, and focus:
\begin{itemize}
\item There are roughly ten graduate students, most actively
  coadvised.
\item In the last five years, the group has produced over twenty papers
  published in ASPLOS, ISCA, PLDI, OOPSLA, MICRO, and OSDI as well as three
  papers in the USENIX Workshop on Hot Topics in Parallelism.
\end{itemize}
The SAMPA group is an ideal size for collaboration across the system
execution stack from computer architecture up through software
engineering.  Compared to large collaborations with several faculty,
there are no graduate students (or faculty) who specialize entirely in
particular subtopics.  The students gain expertise across
computer-science disciplines and use appropriate ideas from hardware,
software, theory, etc. to solve research problems.

@@

\begin{itemize}
\item PI Oskin will focus on communication issues. 
\item PI Ceze will focus on compiler and programming languages work.
\item PI Kahan will focus on organizing benchmarks and performance evaluation efforts.
\item All PIs expect to solicit guidance and collaboration from
  researchers such as John Feo (PNNL), David Callahan (Microsoft, recently moved to PNNL), Jim Larus (Microsoft Research), Hans
  Boehm (HP Research), and Preston Briggs,  with whom
  they have already collaborated on other projects.
\end{itemize}
